Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-03-25 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
outline changes, correcting heating stats section, adding figures, correcting figures

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of electron and ion heating on nanoflare-heated loops. In particular, we look at how the hot emission is affected by heating preferentially one species or the other as well as how this hot emission can vary with heating frequency and the power-law index that determines the event energy distribution. Additionally, we consider how NEI may affect hot emission measure slopes in the cases of electron and ion heating as well as the single-fluid case.

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(3~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 10 different types of heating functions. \hl{Adjust depending on what value of $\beta$ we use in the end.	}}

@@

		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$. The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $\langle T_N\rangle=2000$ s.}

@@

		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=2500$ s. For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}

>>>>

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution. Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and  how NEI may affect hot emission measure slopes.

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions. \hl{Adjust depending on what value of $\beta$ we use in the end.	}}

@@

		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$. The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $\langle t_N\rangle=2000$ s.}

@@

		\caption{Power-law distributions of heating events for indices $\alpha=-1.5,-2.0,-2.5$ for a given heating frequency, $t_N=5000$ s. For each frequency, $t_N$, we compute $N_R$ runs such that the total number of events simulated for each $t_N$ is $N\times N_R\sim10^4$.}
